%!TEX root = ../thesis.tex
\begin{cabstract}
华南师范大学是一所有着悠久历史和深厚人文底蕴的高等学府，学校地处中国改革开放之%
都——广州，深得岭南开放务实之精神，有着素朴的传统和良好的学风，七十多年来，学校坚%
持师范教育的特色，始终致力于培养人格健全、有思想、有能力、有社会责任感的优秀人才。%

在大学日益参与经济社会发展的新世纪，华南师范大学正以崭新的风貌、开阔的世界眼光，%
不断拓展大学的育人理念，创造良好的教学和包容的学术研究环境，营造丰富的校园文化，%
努力构建特色鲜明、开放式、综合性高水平教学研究型大学。%
\end{cabstract}
\ckeywords{华南师范大学；论文；模板}

\begin{eabstract}
  South China Normal University is an institution of higher education with a
  long history and a rich legacy. Situated in Guangzhou, the open metropolis in
  South China, South China Normal University is imbued with Lingnan's
  pioneering and pragmatic spirits. It has developed a tradition of elegant
  simplicity and fostered a strong learning environment. In the past seventy
  years or so, South China Normal University has preserved its characteristics
  of teacher education and has been devoted to cultivating talents with moral
  integrity, independent thinking, innovative ability and sense of social
  responsibility.

  In the new century in which the institutions of higher education are getting
  increasingly involved in the social and economic development, South China
  Normal University has adopted an international view on education. Having
  broadened its horizon on the key issue of cultivating talents, it has made its
  greatest efforts to create a congenial and harmonious environment for both
  teaching and academic research and has fostered a rich variety of campus
  culture. It aims to build itself into a high-level comprehensive teaching and
  research-oriented university with open distinctive features.
\end{eabstract}
\ekeywords{SCNU; thesis; template}

